Understanding and Verifying the Shape of Stencil Computations

### 2017-03-29 oopsla17/lattice-model.tex
Factor macros used in lattice model out
Remove redundant comment
change to cartesian product and pi for projection notation

% Essential packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{xifthen}

% Non-essential
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

@@

% Auxillary declaration
\newcommand{\eg}{\emph{e.g.}}

% Essential macros
\newcommand{\zinf}{\textnormal{$\mathbb{Z}_\infty$}}
\newcommand{\interp}[1]{\llbracket{} {#1} \rrbracket{}}
\newcommand{\interv}[3]{\textnormal{$\lbrack#1,#2\rbrack^{#3}$}}
\newcommand{\vecgen}[3]{\textnormal{$\textit{vec-gen}_{#1}(#2,#3)$}}
\newcommand{\textcap}[1]{\texttt{\textit{#1}}}

% Stencil macro
%
% Optional argument: s when we want the short form, empty otherwise.
%
% Mandatory arguments:
% 1st: c/b/f/p for centered, backward, forward, pointed
% 2st: dimension
% 3st: depth
% 4st: if pointed/nonpointed needs to be specified leave it blank if omitted.
%
% Example: \stencil[s]{f}{1}{2}{} = fwd(dim=1,depth=2)
% Example: \stencil{b}{1}{2}{pointed} = backward(dim=1,depth=2,pointed)
\newcommand{\stencil}[5][]{%
  \ifthenelse{\equal{#2}{f}}{%
    \ifthenelse{\equal{#1}{s}}{%
      \texttt{fwd}%
    }{\ifthenelse{\isempty{#1}}{%
        \texttt{forward}%
      }{INVALID OPTIONAL}%
    }%
  }{\ifthenelse{\equal{#2}{b}}{%
      \ifthenelse{\equal{#1}{s}}{%
          \texttt{bwd}%
      }{\ifthenelse{\isempty{#1}}{%
          \texttt{backward}%
        }{INVALID OPTIONAL}%
      }%
  }{\ifthenelse{\equal{#2}{c}}{%
      \ifthenelse{\equal{#1}{s}}{%
          \texttt{ctd}%
      }{\ifthenelse{\isempty{#1}}{%
          \texttt{centered}%
        }{INVALID OPTIONAL}%
      }%
  }{\ifthenelse{\equal{#2}{p}}{%
      \ifthenelse{\equal{#1}{s}}{%
          \texttt{ptd}%
      }{\ifthenelse{\isempty{#1}}{%
          \texttt{pointed}%
        }{INVALID OPTIONAL}%
      }%
  }{\ifthenelse{\isempty{#1}}{%
      \textcap{#2}%
    }{NO OPTIONAL FOR CUSTOM}%
  }}}}%
  \texttt{(dim=\textnormal{#3}%
    \ifthenelse{\isempty{#4}}{}{,depth=\textnormal{#4}}%
    \ifthenelse{\isempty{#5}}{}{,\textnormal{#5}})}%
}

% Non-essential macro
\definecolor{unused}{RGB}{211,167,192}
\newcommand{\unused}[1]{{\color{unused} #1}}

\definecolor{version}{RGB}{163,193,173}
\newcommand{\longv}[1]{{\color{version} Long version:} #1}
\newcommand{\shortv}[1]{{\color{version} Short version:} #1}

@@

\begin{defn}{(\emph{Offset space})}
  \emph{Offset space} is a subset of \zinf{} members. It is used to capture
  offsets from induction variables.

%  $\mathcal{P}(\zinf{})$ couple with $\supseteq$ is the power set distributive
%  lattice.
\end{defn}

@@

\begin{defn}{(\emph{Offsets vector})}
  An \emph{offsets vector} is a $N$ dimensional vector of offset spaces denoted
  by $(\textit{offs}_1, \dots, \textit{offs}_N)$ to mean $\textit{offs}_1 \times
  \dots \times \textit{offs}_N$.

@@

\begin{lem}{}\label{lem:vector-intersect}
  Intersection distributes over offsets vectors.
%
  \begin{equation*}
    (\textit{vint}_1, \dots, \textit{vint}_N) \;\cap\;
      (\textit{vint'}_1, \dots, \textit{vint'}_N)
      =
    (\textit{vint}_1 \;\cap\; \textit{vint'}_1, \dots,
     \textit{vint}_N \;\cap\; \textit{vint'}_N)
  \end{equation*}
\end{lem}
%
\begin{proof}
  \begin{align*}
    v \; \cap \; v' &
    = \{x \mid \bigwedge_{1 \leq i \leq N } x_i \in v_i \}
      \;\cap\;
      \{x \mid \bigwedge_{1 \leq i \leq N } x_i \in v'_i \} \\
    & = \{x \mid \bigwedge_{1 \leq i \leq N } (x_i \in v_i \wedge x_i \in v'_i) \} \\
    & = (v_1 \cap v'_1,\dotsc,v_N \cap v'_N)
  \end{align*}
\end{proof}

\begin{lem}{}\label{lem:vector-union}
  Let $v$ and $v'$ be two $N$ dimensional offsets vectors such that $v_i$ is
  equal to $v'_i$ for all $1 \leq i \leq N$ except $k$, then we have the
  following:
%
  \begin{equation*}
    (v_1,\dotsc, v_k,\dotsc, v_N) \; \cup \; (v'_1,\dotsc, v'_k, \dotsc, v_N)
    =
    (v_1,\dotsc, v_k \cup v'_k,\dotsc, v_N)
  \end{equation*}
\end{lem}
%
\begin{proof}
  \begin{align*}
    v \; \cup \; v' &
    = \{x \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v_i \}
      \;\cup\;
      \{x \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v'_i \} \\
    & = \{x \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
              \wedge x_k \in v_k \vee
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v'_i
            \wedge x_k \in v'_k
        \} \\
    & = \{x \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
          \wedge x_k \in v_k \cup v'_k
        \} \\
    & = (v_1,\dotsc, v_k \cup v'_k,\dotsc, v_N)
  \end{align*}
\end{proof}

\begin{defn}{(\emph{Vector interval})}
  A vector interval is an $N$ dimensional object which has \zinf{} intervals at
  each dimension. It is denoted with $(\textit{int}_1, \dots, \textit{int}_n)$,
  where $\textit{int}_i$ is a \zinf{} interval. If \textit{vint} is a vector
  interval, $\textit{vint}_i$ denotes the \zinf{} interval at the $i^{th}$
  dimension.

  The set of $N$ dimensional vector intervals is $\textit{Interval}^N$. Every
  vector interval is also an offsets vector.
\end{defn}

@@

We give some basic interpretations: $\interp{\texttt{n}} = n$ where $n$ is in
$\mathbb{Z}^+$, $\interp{\texttt{pointed}} = \llbracket \epsilon \rrbracket =
\textsf{true}$, $\interp{\texttt{nonpointed}} = \textsf{false}$.
Typographically, cursive monotype font is used within specifications to indicate
a partial textual capture. For convenience we use \textit{italic} serif font
inside specifications rather than interpreting its textual capture. This
coalesces syntactic and semantic representation but avoids clutter in the
presentation.

>>>>

% Essential packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{stencilmacros}

@@

@@

\begin{defn}{(\emph{Offset space})}
  \emph{Offset space} is a subset of \zinf{} members. It is used to capture
  offsets from induction variables.
\end{defn}

@@

\begin{defn}{(\emph{Offsets vector})}
  An $N$ dimensional \emph{offsets vector} is a Cartesian product of offset
  spaces denoted with $\textit{offs}_1 \times \dots \times \textit{offs}_N$.
  The function $\pi_i : \zinf{}^{\mkern-19mu{N}} \to \zinf{}$ retrieves the
  $i^{th}$ set of offsets.

@@

\begin{lem}{}\label{lem:vector-intersect}
  Intersection distributes over offsets vectors. If $v$ and $v'$ are $N$
  dimensional ofssets vectors, then
%
  \begin{equation*}
    v \cap v' = \prod_{i = 1}^{N} \pi_i(v) \cap \pi_i(v')
  \end{equation*}
\end{lem}
%
\begin{proof}
  \begin{align*}
    v \; \cap \; v' &
    = \{x \mid \bigwedge_{1 \leq i \leq N } x_i \in v_i \}
      \;\cap\;
      \{x \mid \bigwedge_{1 \leq i \leq N } x_i \in v'_i \} \\
    & = \{x \mid \bigwedge_{1 \leq i \leq N } (x_i \in v_i \wedge x_i \in v'_i) \} \\
    & = \prod_{i = 1}^{N} \pi_i(v) \cap \pi_i(v')
  \end{align*}
\end{proof}

\begin{lem}{}\label{lem:vector-union}
  Let $v$ and $v'$ be two $N$ dimensional offsets vectors such that $\pi_i(v)$
  is equal to $\pi_i(v')$ for all $1 \leq i \leq N$ except $k$, then we have the
  following:
%
  \begin{equation*}
    v \; \cup \; v'
    =
    \pi_1(v) \times \cdots \times
    (\pi_k(v) \cup \pi_k(v')) \times \cdots \times
    \pi_N(v)
  \end{equation*}
\end{lem}
%
\begin{proof}
  \begin{align*}
    v \; \cup \; v' &
    = \{x \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v_i \}
      \;\cup\;
      \{x \mid
          \bigwedge_{1 \leq i \leq N } x_i \in v'_i \} \\
    & = \{x \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
              \wedge x_k \in v_k \vee
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v'_i
            \wedge x_k \in v'_k
        \} \\
    & = \{x \mid
          \bigwedge_{\substack{1 \leq i \leq N \\ i \neq k}} x_i \in v_i
          \wedge x_k \in v_k \cup v'_k
        \} \\
    & = \pi_1(v) \times \cdots \times
        (\pi_k(v) \cup \pi_k(v')) \times \cdots \times
        \pi_N(v)
  \end{align*}
\end{proof}

\begin{defn}{(\emph{Vector interval})}
  A vector interval is an $N$ dimensional object which has \zinf{} intervals at
  each dimension. A vector interval is also an ofssets vector.

  The set of all $N$ dimensional vector intervals is $\textit{Interval}^N$.
\end{defn}

@@

We give some basic interpretations: $\interp{\texttt{n}} = n$ where $n$ is in
$\mathbb{Z}^+$, $\interp{\texttt{pointed}} = \llbracket \epsilon \rrbracket =
\textsf{true}$, $\interp{\texttt{nonpointed}} = \textsf{false}$.
Typographically, \textcap{italic monotype font} is used within specifications
to indicate a partial textual capture. For convenience, we use \textit{italic
serif font} inside specifications rather than interpreting its textual capture.
This coalesces syntactic and semantic representation but avoids clutter in the
presentation.
